---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
* After reading the table, I'll check what each column is.
```{r}
setwd("/Users/jinyang/RepData_PeerAssessment1")
data <- read.csv("activity.csv")
head(data)

```

## What is mean total number of steps taken per day?
* Steps taken per day is recorded in column 1
```{r}
u <- is.na(data[,1])
data_clean <- data[!u,]
data_sum <- aggregate(steps~date,sum,data = data_clean)
hist(data_sum[,2],col="gray",main = paste("Histograom of daily step"),xlab="total steps every day")
data_mean <- aggregate(steps~date,mean,data = data_clean)
data_median <- aggregate(steps~date,median,data = data_clean)
data_mean
data_median

```

## What is the average daily activity pattern?
```{r}
data_intervmean <-aggregate(steps~interval,mean,data=data_clean)
plot(data_intervmean[,1],data_intervmean[,2],type = "l",main = "Plot of steps at different intervals", xlab="Interval, min", ylab = "Steps averaged over all days")

a<- max(data_intervmean[,2])
b<- match(c(a),data_intervmean[,2])
Intervalmax <- data_intervmean[b,1]
Intervalmax
```
* The interval that has the maximum steps is `Intervalmax` min.

## Imputing missing values
```{r}
mising_sum <- sum(u)
data2<-data
for (i  1:length(data2))
{    if (is.na(data2[i,1]))
    {   inte<-data2[i,3]
        c<-match(c(int),data_intervmean[,1])
        data2[i,1]<-data_intervmean[c,2]
    }
}

```

## Are there differences in activity patterns between weekdays and weekends?
```{r}
data3 <- data
for(i in 1:length(data3))
  {
  data3[i,4]<-weekday(data3[i,2])
  }
